Education and the Rate of Entrepreneurship - Data Gathering and Analysis

### 2014-11-14 GEMDataSource.Rmd
Edits to markdown for consistency, organized repository, and created new README

---
title: Education and the Rate of Entrepreneurship - Data Gathering and Analysis
author: "Samuel Dundon and Thierry Racaud"
date: "November 14, 2014"
output: html_document
---
***

@@

We have examined three dimensions of entrepreneurship to prepare for this stage of the project. We have analyzed established entrepreneurship in the country, nascent entrepreneurship (less than three months), and entrepreneurial intention. We will study them successively as we may well observe different effects.

@@

We chose the GEM measure of entrepreneurship, as it is often referred to, especially in OECD studies.

@@

As Inglehart has shown how personal values are shaped before the age of 20, we will try to show how compulsory education (from 6 to 16 years of age) shapes individuals, especially in terms of self-esteem. Of course, is is not easy to quantify how supportive of students' self-esteem a given education system can be and we are still looking for the most adequate measure.

To begin with, we decided to incorporate to GEM indicators that relate to self-esteem and confidence. First, included GEM survey data on the average "perceived capabilities" of an individual (18-64) of a given country to start a business. The data consists of average percentage at country-level. Second, we included additional GEM data on how the "fear of failure" could deter the average individual (18-64) of a country to become an entrepreneur. The data consists of average percentage at country-level.

@@

To control for the general state of the economy globally and in each country, we included Annual GDP Growth from the World Bank as a control variable in our regression equations.  We first considered including real GDP, but decided to include growth to more accurately capture fluctuation in the economy.  In addition, we included a GEM indicator called "Perceived Opportunities." For each country, it is the average percentage of individuals who believe there are opportunities to start a business in the area they live in. Since we look at average individual self-esteem in every OECD country, we believe it is appropriate to look at the opportunities perceived by the average 18-64-year-old individual of these countries.

In the future, we may include lagged GDP growth in recognition of the time taken for governments and individuals to react to the state of the economy, and are planning to include several control variables from GEM. Specifically, we intend to control for the classic determinants of entrepreneurship -- economic and structural determinants. To do so, we will add the following nine key entrepreneurship conditions as defined in the GEM [National Experts Survey (NES)](http://http://www.gemconsortium.org/Data-Collection) that may affect the rate of entrepreneurship.

@@

To collect the data necessary to run these regression equations, we downloaded *.csv* data from GEM and used the WDI API to obtain the necessary Annual GDP growth of OECD Countries.

@@

As mentioned above, one of our control variables, annual GDP growth, was obtained using the [World Development Indicators](http://data.worldbank.org/data-catalog/world-development-indicators) API from the World Bank.  Using this API, we accessed GDP data from all the OECD countries directly from R and R will pull this information from WDI whenever this code is run. To clean this data, we used plyr to change the variable names then recoded the U.S. and South Korea country names to maintain consistency with the GEM data set and dropped an unnecessary column that was not included with the GEM data.

Finally, we merged the annual GDP growth data with the *FinalGEM* data set to create *CompleteDataset*.  This is the data set used to run the regressions and generate the charts and figures outlined in this report.  To reduce complexity in the environment we also included a command to remove unnecessary objects from the environment (all the individual original and cleaned GEM data, and the intermediate merged data sets used to create *FinalGEM*)

@@

To examine the relationship between these variables, we used least square estimation, the results of which can be found in the following table.  The package *stargazer* was required to generate this table.  As evidenced by the equation results, the individual variables selected are statistically significant, but the model only explains a relatively small degree of the variation in the dependent variable.  For example, the adjusted $R^2$ of regression equation one is .29, the adjusted $R^2$ of regression equation two is .38, and the adjusted $R^2$ is .13.  
<br>

@@

### Summary

@@

### References

>>>>

---
title: "Education and the Rate of Entrepreneurship - Data Gathering and Analysis"
author: "Samuel Dundon and Thierry Racaud"
date: "November 14, 2014"
output: html_document
---
***

@@

We have examined three dimensions of entrepreneurship to prepare for this stage of the project, established entrepreneurship in the country, nascent entrepreneurship (less than three months), and entrepreneurial intention. We will study each of these successively as we may well observe different effects.

@@

@@

As Inglehart has shown how personal values are shaped before the age of 20, we will try to show how compulsory education (from 6 to 16 years of age) shapes individuals, especially in terms of self-esteem. To do so, we decided to incorporate GEM indicators that relate to self-esteem and confidence. First, we included GEM survey data on the average "perceived capabilities" of an individual (18-64) in a given country to start a business. Second, we included additional GEM data on how the "fear of failure" could deter an average individual (18-64) in a country to become an entrepreneur. Both of these data sets indicate the average percentage for each characteristic at the country-level.

@@

To control for the general state of the economy, we included annual GDP Growth from the World Bank [World Development Indicators](http://data.worldbank.org/data-catalog/world-development-indicators) as a control variable in our regression equations.  In addition, we included a GEM indicator called "Perceived Opportunities." For each country, it is the average percentage of individuals who believe there are opportunities to start a business in their area. Since we look at average individual self-esteem in every OECD country, we believe it is appropriate to look at the opportunities perceived by the average 18-64-year-old individual in these countries.

In the future, we may revise this to include lagged GDP growth in recognition of the time taken for governments and individuals to react to the state of the economy, and are planning to include control variables from GEM. Specifically, we intend to control for the classic determinants of entrepreneurship -- economic and structural determinants. To do so, we will add the following nine key entrepreneurship conditions as defined in the GEM [National Experts Survey (NES)](http://http://www.gemconsortium.org/Data-Collection).

@@

To collect the data necessary to run these regression equations, we downloaded *.csv* data from GEM and used the WDI API to obtain the necessary annual GDP growth of OECD Countries.

@@

As mentioned above, one of our control variables, annual GDP growth, was obtained using the WDI API from the World Bank.  Using this API, we accessed GDP data from all the OECD countries directly from *R*. To clean this data, we used *plyr* to change the variable names then recoded the U.S. and South Korea country names to maintain consistency with the GEM data set and dropped an unnecessary column that was not included with the GEM data.

Finally, we merged the annual GDP growth data with the *FinalGEM* data set to create *CompleteDataset*.  This is the data set used to run the regressions and generate the charts and figures outlined in this document.  To reduce complexity in the environment we also included a command to remove unnecessary objects in the environment.

@@

To examine the relationship between these variables, we used least square estimation, the results of which can be found in the following table.  The package *stargazer* was required to generate this table.  As evidenced by the equation results, the individual variables selected are statistically significant, but the model only explains a relatively small degree of the variation in the dependent variable.  For example, the adjusted $R^2$ of regression equation one is 0.29, the adjusted $R^2$ of regression equation two is 0.38, and the adjusted $R^2$ is 0.13.  
<br>

@@

#### Summary

@@
